Contract tracing, simply put, is the process of identifying all people that a COVID-19 patient has come in contact with in the last two weeks.

https://smittestop.dk/about-the-app/ :
Smittestop app:
-	It helps to contain the spread of COVID-19 in Denmark
-	Can anonymously warn others that they have been in contact with COVID-19

-	Essential part of transitioning back to daily life, and managing further outbreaks
-	The app makes your phone send out Bluetooth signals (IDs) to nearby phones. Your phone registers other nearby people’s phones, with whom you’ve had close contact to.
-	If an app user you’ve had close contact with is diagnosed with COVID, the app will notify you.
-	Furthermore, the app will help you on what precautions you should take, and what to do from here.
-	And vice versa you yourself can report that you have been diagnosed with COVID-19, then others you have been in contact with gets notified.

-	GDPR? There is no personal information shared between app users, and there is no telling where and when you were with a person diagnosed with COVID-19


How it works:
-	 The app will generate a random device ID every 10-20 minutes. Your phone and others will exchange these IDs via Bluetooth, in the background.
-	Your phone will regularly check all the IDs associated with a positive COVID-19 case against the your phones own ID list(the exchanged IDs). If there is a match, then you will be notified on what to do next form the Danish health authorities.

-	If you tested positive, then you can use your nemID to confirm your positive results. You will then be asked if you experienced any symptoms 


https://nyheder.tv2.dk/samfund/2020-09-28-smittestop-app-laves-om-efter-fejl :

-	Der var fejl I appen
-	Den er downloaded af 1.500.000
-	Folk bliver informeret inden for 2 dage før symptomer og 8 dage efter.

styrelsen for patientsikkerhed
https://stps.dk/da/om-os/data-og-privatlivspolitik/smitteapp-privatliv/#

https://www.cdc.gov/coronavirus/2019-ncov/php/contact-tracing/contact-tracing-plan/contact-tracing.html

WHO om contact tracing
https://www.who.int/news-room/feature-stories/detail/tracking-covid-19-contact-tracing-in-the-digital-age#:~:text=contact%20tracing%20is%20the%20process,the%20last%20two%20weeks.